Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is ??? to ??? in the x-direction, and ??? - ??? in the
  y-direction, in heliocentric cartesian co-ordinates
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
  black lines indicate the 3 and 5 minute frequencies.}
\label{fig:compare171193}
\end{figure}

>>>>

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is ??? to ??? in the x-direction, and ??? - ??? in the
  y-direction, in heliocentric cartesian co-ordinates
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\centerline{
\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
}
\centerline{
\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
}
\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
  black lines indicate the 3 and 5 minute frequencies.}
\label{fig:compare171193}
\end{figure}
